---
title: "Cabbages"
author: "Adriana Pimentel"
date: "09/04/2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```
  
The box plot shows that the cultivation method, c52, has a greater amount of vitamin c than the cultivation method c39. The median of c52 is about 65 and the median of c39 is about 51. Meaning that, the 25 percentile of c52 is greater than the 75 percentile of c39, which proves that c52 produces more vitamin c than c39.    
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```
    
The average amount of vitamin c produced in c39 is 51.5. The average amount of vitamin c produced in c52 is 64.4. This assures that on average, c52 produces more vitamin c than c39, justifying the previous statement.    
    
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
    
The p-value is 0.00000003405. Which represents the chances that we would get these specific results if the null hypothesis was true. So, if the null hypothesis is true, then, there is a 0.00000003405% of getting the same results. Since, this number of receiving the specific results is so small, we choose to reject the null hypothesis.   
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
In conclusion, we first had to figure out what type of problem we had in order to put up the correct helper file. We learned that we needed a numerical explained by a categorical helper file. So, we uploaded the helper file, Numerical~Cat.rmd file into Rstudio. Then we imported the function in the helper file onto the problem file to graphically compare c52 and c39 using a box plot. After that, we imported a favstats function to compare the sets numerically and explain the means of each sets. Lastly, we imported a t.test function to explain the p-value given. Since, the p-value was so small we decided to reject the null hypothesis.    
  